---
title: "7-20"
output: html_document
---

#Load data and package
```{r}
SEED <- 2019
library(scCB2)
library(DropletUtils)

load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/PBMC68K.RData")
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/UW.RData")
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/MALT.RData")
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/mbrain.RData")
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/PBMC1K.RData")
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/PBMC8K.RData")
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/sim/sim_bg_new.RData")

sessionInfo()
```

#Define functions

```{r}
reorder_mat <- function(mat, rate = 0.1) {
  N_row <- as.integer(nrow(mat) * rate)
  x <- 1:nrow(mat)
  reorder_row <- sample(x, N_row)
  x[sort(reorder_row)] <- reorder_row
  return(mat[x, ])
}

#This function refers to EmptyDrops' background simulation codes
SIMFUN_bg <- function(raw.mat,  
                      threshold = 100,
                      remove_protein = T) {
  # For Cell Ranger version >=3, proteins will be removed.
  # Reasons are discussed in CB2 paper and scCB2 package.
  if (remove_protein) {
    protein <- grep(pattern = "TotalSeqB", x = rownames(raw.mat))
    if (length(protein) > 0) {
      raw.mat <- raw.mat[-protein, ]
    }
  }
  
  stats <- barcodeRanks(raw.mat, lower = threshold)
  
  # Assuming all cells below the inflection point are empty droplets.
  totals <- stats$total
  empty.limit <- stats@metadata$inflection
  ambient.prof <- rowSums(raw.mat[, totals <= empty.limit])
  empty.totals <- totals[totals <= empty.limit]
  
  # Scrambling to generate resampled empty droplets.
  gene.ids <- rep(seq_along(ambient.prof), ambient.prof)
  gene.ids <- sample(gene.ids)
  cell.ids <- rep(seq_along(empty.totals), empty.totals)
  resampled <-
    makeCountMatrix(gene.ids, cell.ids, all.genes = rownames(raw.mat))
  colnames(resampled) <- paste0("bg_", 1:ncol(resampled))
  
  # Completed.
  return(resampled)
}

SIM2 <-
  function(n = 5,
           dat,
           dat_bg = NULL,
           threshold = 100,
           n_large = 2000,
           n_middle = 2000,
           n_small = 2000,
           new_sim = T,
           remove_protein = T,
           FDR = 0.01,
           reorder_rate = 0.1,
           threegroup = T,
           ...) {
    if (remove_protein) {
      protein <- grep(pattern = "TotalSeqB", x = rownames(dat))
      if (length(protein) > 0) {
        dat <- dat[-protein, ]
      }
    }
    brank <- barcodeRanks(dat, lower = threshold)
    inflection <-
      ifelse(is.null(brank$inflection),
             brank@metadata$inflection,
             brank$inflection)
    
    ###background barcodes
    if (is.null(dat_bg)) {
      dat_bg <- SIM_bg(dat, threshold = threshold)
    }
    
    all_bg <- sum(Matrix::colSums(dat) %in% 1:inflection)
    th_bg <- sum(Matrix::colSums(dat) %in% (threshold + 1):inflection)
    
    dat_true1 <- dat[, Matrix::colSums(dat) > inflection]
    
    TP_CB2 <- matrix(0, 6, n + 1)
    colnames(TP_CB2) <- c(paste0("rep", 1:n), "Ave")
    rownames(TP_CB2) <-
      c("G1", "G1 prop", "G2", "G2 prop", "G3", "G3 prop")
    
    FP_CB2 <- TP_CB2[1:4, ]
    rownames(FP_CB2) <-
      c(
        paste0("all (", all_bg, ")"),
        "all prop",
        paste0(">", threshold, " (", th_bg, ")"),
        paste0(">", threshold, " prop")
      )
    
    TP_ED <- TP_CB2
    FP_ED <- FP_CB2
    
    SEED.rep <- as.integer(runif(n, 1, 100000))
    
    for (sss in 1:n) {
      SEED.tmp <- SEED.rep[sss]
      
      cat(paste0("Run ", sss, "\n"))
     
      set.seed(SEED.tmp)

      ###2000 G1 large cells
      G1 <- dat_true1[, sample(ncol(dat_true1), n_large, replace = T)]
      colnames(G1) <- paste0("G1_", 1:ncol(G1))
      G1 <- as(G1, "dgCMatrix")
      
      if (threegroup) {
        ###2000 G2 middle cells (50% downsampling)
        G2 <- dat_true1[, sample(ncol(dat_true1), n_middle, replace = T)]
        G2 <- as(G2, "dgCMatrix")
        G2 <- downsampleMatrix(G2, 0.5)
        colnames(G2) <- paste0("G2_", 1:ncol(G2))
      }
      
      ###2000 G3 small cells (10% downsampling)
      G3 <- dat_true1[, sample(ncol(dat_true1), n_small, replace = T)]
      G3 <- as(G3, "dgCMatrix")
      G3 <- downsampleMatrix(G3, 0.1)
      colnames(G3) <- paste0("G3_", 1:ncol(G3))
      
      if (new_sim) {
        G1 <- reorder_mat(G1, rate = reorder_rate)
        if (threegroup)
          G2 <- reorder_mat(G2, rate = reorder_rate)
        G3 <- reorder_mat(G3, rate = reorder_rate)
      }

      if (threegroup) {
        dat_sim1 <- cbind(dat_bg, G1, G2, G3)
      } else{
        dat_sim1 <- cbind(dat_bg, G1, G3)
      }
      
      
      
      set.seed(SEED.tmp)

      res_CB2 <-
          CB2FindCell(dat_sim1,
              pooling_threshold = threshold,
              FDR_threshold = FDR,
              ...)

      res1 <- colnames(GetCellMat(res_CB2))

      TP_CB2[1, sss] <- length(grep(x = res1, pattern = "G1"))
      TP_CB2[2, sss] <- TP_CB2[1, sss] / n_large
      
      TP_CB2[3, sss] <- length(grep(x = res1, pattern = "G2"))
      TP_CB2[4, sss] <- TP_CB2[3, sss] / n_middle
      
      TP_CB2[5, sss] <- length(grep(x = res1, pattern = "G3"))
      TP_CB2[6, sss] <- TP_CB2[5, sss] / n_small
      
      FP_CB2[1, sss] <- length(grep(x = res1, pattern = "bg"))
      FP_CB2[2, sss] <- FP_CB2[1, sss] / all_bg
      
      FP_CB2[3, sss] <- length(grep(x = res1, pattern = "bg"))
      FP_CB2[4, sss] <- FP_CB2[3, sss] / th_bg
      
      eOut <- emptyDrops(dat_sim1, lower = threshold)
      sim_ED <- dat_sim1[, ifelse(is.na(eOut$FDR), FALSE, eOut$FDR <= FDR)]
      res_ED2 <- colnames(sim_ED)
      
      TP_ED[1, sss] <- length(grep(x = res_ED2, pattern = "G1"))
      TP_ED[2, sss] <- TP_ED[1, sss] / n_large
      
      TP_ED[3, sss] <- length(grep(x = res_ED2, pattern = "G2"))
      TP_ED[4, sss] <- TP_ED[3, sss] / n_middle
      
      TP_ED[5, sss] <- length(grep(x = res_ED2, pattern = "G3"))
      TP_ED[6, sss] <- TP_ED[5, sss] / n_small
      
      FP_ED[1, sss] <- length(grep(x = res_ED2, pattern = "bg"))
      FP_ED[2, sss] <- FP_ED[1, sss] / all_bg
      
      FP_ED[3, sss] <- length(grep(x = res_ED2, pattern = "bg"))
      FP_ED[4, sss] <- FP_ED[3, sss] / th_bg
    }
    
    TP_CB2[, n + 1] <- rowMeans(TP_CB2[, 1:n])
    TP_ED[, n + 1] <- rowMeans(TP_ED[, 1:n])
    FP_CB2[, n + 1] <- rowMeans(FP_CB2[, 1:n])
    FP_ED[, n + 1] <- rowMeans(FP_ED[, 1:n])
    
    Stat <- matrix(NA, 2, 2)
    colnames(Stat) <- c("CB2", "ED")
    rownames(Stat) <- c("Power", "FDR")
    Stat[1, 1] <-
      (TP_CB2[2, n + 1] * n_large + TP_CB2[4, n + 1] * n_middle + TP_CB2[6, n + 1] * n_small) / (n_large + n_middle + n_small)
    Stat[1, 2] <-
      (TP_ED[2, n + 1] * n_large + TP_ED[4, n + 1] * n_middle + TP_ED[6, n + 1] * n_small) / (n_large + n_middle + n_small)
    Stat[2, 1] <-
      FP_CB2[3, n + 1] / (FP_CB2[3, n + 1] + Stat[1, 1] * (n_large + n_middle + n_small))
    Stat[2, 2] <-
      FP_ED[3, n + 1] / (FP_ED[3, n + 1] + Stat[1, 2] * (n_large + n_middle + n_small))
    Power_diff <- Stat[1, 1] - Stat[1, 2]
    
    return(
      list(
        TP_CB2 = TP_CB2,
        FP_CB2 = FP_CB2,
        TP_ED = TP_ED,
        FP_ED = FP_ED,
        Stat = Stat,
        Power_diff = Power_diff
      )
    )
  }

```

#Run simulation under easy setting

Under easy setting, part of genes in real cells are shuffled so that they are more different from background, making them easier to be tested out.

```{r}
set.seed(SEED)
MALT_SIM <- SIM2(dat = MALT_r,dat_bg = MALT_bg, new_sim = T,Ncores=4)

set.seed(SEED)
mbrain_SIM <- SIM2(dat = mbrain_r,dat_bg = mbrain_bg, new_sim = T,Ncores=4)

set.seed(SEED)
PBMC1K_SIM <- SIM2(dat = PBMC1K_r,dat_bg = PBMC1K_bg,new_sim = T,Ncores=4)

set.seed(SEED)
PBMC68K_SIM <- SIM2(dat = PBMC_r,dat_bg = PBMC_bg,new_sim = T,Ncores=4)

set.seed(SEED)
UW_SIM <- SIM2(dat = UW_r,dat_bg = UW_bg,new_sim = T,Ncores=4)

set.seed(SEED)
PBMC8K_SIM <- SIM2(dat = PBMC8K_r,dat_bg = PBMC8K_bg,new_sim = T,Ncores=4)

save(MALT_SIM,mbrain_SIM,PBMC1K_SIM,PBMC68K_SIM,PBMC8K_SIM,UW_SIM,file = "~/Google Drive/Hallu/codes/ckgroup/DropletUtils/sim/sim_7_20_cor_newSim_scCB2.RData")
```

#Run simulation under hard setting (no shuffling genes)

Under hard setting, genes in simulated real cells are not shuffled. This is closer to real world. 

```{r}
set.seed(SEED)
MALT_SIM <- SIM2(dat = MALT_r,dat_bg = MALT_bg, new_sim = F,Ncores=4)

set.seed(SEED)
mbrain_SIM <- SIM2(dat = mbrain_r,dat_bg = mbrain_bg, new_sim = F,Ncores=4)

set.seed(SEED)
PBMC1K_SIM <- SIM2(dat = PBMC1K_r,dat_bg = PBMC1K_bg,new_sim = F,Ncores=4)

set.seed(SEED)
PBMC68K_SIM <- SIM2(dat = PBMC_r,dat_bg = PBMC_bg,new_sim = F,Ncores=4)

set.seed(SEED)
UW_SIM <- SIM2(dat = UW_r,dat_bg = UW_bg,new_sim = F,Ncores=4)

set.seed(SEED)
PBMC8K_SIM <- SIM2(dat = PBMC8K_r,dat_bg = PBMC8K_bg,new_sim = F,Ncores=4)

save(MALT_SIM,mbrain_SIM,PBMC1K_SIM,PBMC68K_SIM,UW_SIM,PBMC8K_SIM,file = "~/Google Drive/Hallu/codes/ckgroup/DropletUtils/sim/sim_7_20_cor_oldSim_scCB2.RData")
```



##plot
```{r}
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/sim/sim_7_20_cor_oldSim_scCB2.RData")

#load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/sim/sim_7_20_cor_newSim_scCB2.RData")

library(ggplot2)
RED <- "#FF9999"
BLUE <- "#56B4E9"
GREEN <- "#009E73"
YELLOW <- "#F0E442"

Res_list <- list()
Res_list[[1]] <- MALT_SIM
Res_list[[2]] <- mbrain_SIM
Res_list[[3]] <- PBMC1K_SIM
Res_list[[4]] <- PBMC68K_SIM
Res_list[[5]] <- PBMC8K_SIM
Res_list[[6]] <- UW_SIM

G1E <- unlist(lapply(Res_list,function(x) x$TP_CB2[2,ncol(x$TP_CB2)]))
G1ED <- unlist(lapply(Res_list,function(x) x$TP_ED[2,ncol(x$TP_ED)]))
G2E <- unlist(lapply(Res_list,function(x) x$TP_CB2[4,ncol(x$TP_CB2)]))
G2ED <- unlist(lapply(Res_list,function(x) x$TP_ED[4,ncol(x$TP_ED)]))
G3E <- unlist(lapply(Res_list,function(x) x$TP_CB2[6,ncol(x$TP_CB2)]))
G3ED <- unlist(lapply(Res_list,function(x) x$TP_ED[6,ncol(x$TP_ED)]))
FDR_E <- unlist(lapply(Res_list,function(x) x$Stat[2,1]))
FDR_ED <- unlist(lapply(Res_list,function(x) x$Stat[2,2]))
Power_Inc <- unlist(lapply(Res_list,function(x) x$Power_diff))



NM <- c("MALT","mbrain")
NM <- c("MALT","mbrain","PBMC1K","PBMC68K","PBMC8K","UW")

plot(rep(2,length(NM))~factor(NM),ylim=c(0,1),ylab="power",xlab=NULL)
lines(G1E~factor(NM),col=RED)
lines(G1ED~factor(NM),col=GREEN)
lines(G2E~factor(NM),col=RED,lty=2)
lines(G2ED~factor(NM),col=GREEN,lty=2)
lines(G3E~factor(NM),col=RED,lty=3)
lines(G3ED~factor(NM),col=GREEN,lty=3)
legend(2,0.3,lty=c(1,1,1,2,3),col=c(RED,GREEN,"black","black","black"),legend=c("CB2","EmptyDrops","G1 (large)","G2 (medium)","G3 (small)"),cex = 0.7)

plot(rep(200,length(NM))~factor(NM),ylim=range(Power_Inc)*100,ylab="power diff (%) (CB2 - ED)",xlab=NULL)
lines(Power_Inc*100~factor(NM),col=RED)
abline(h=0,lty=2)
 
plot(rep(100,length(NM))~factor(NM),type="l",ylim=c(0,5),ylab="FDR (%)")
lines(FDR_E*100~factor(NM),col=RED)
lines(FDR_ED*100~factor(NM),col=GREEN)
abline(h=1,lty=2)
legend("topright",lty=1,col=c(RED,GREEN),legend=c("CB2","EmptyDrops"))



```

#Extra functions for drawing plots in CB2 paper
```{r}
#str(G1E)
sim_plot <- data.frame(Power=c(G1E,G1ED,G2E,G2ED,G3E,G3ED),Group=rep(c("G1","G2","G3"),each=12),
                       Method=rep(rep(c("CB2","EmptyDrops"),each=6),3),Dataset=rep(NM,6))
FDR_plot <- data.frame(FDR=c(FDR_E,FDR_ED),Dataset=NM,Method=rep(c("CB2","EmptyDrops"),each=6))
ggplot(data=FDR_plot,aes(y=FDR*100,x=Dataset))+geom_col(aes(fill=Method),position="dodge")+geom_hline(yintercept = 1,linetype="dashed")+ylab("FDR (%)")+ylim(c(0,2))+labs(title="FDR")+
  scale_x_discrete(limits=sort(NM,decreasing = T))+coord_flip()

temp <- "MALT"
temp_plot <- sim_plot[sim_plot$Dataset==temp,]
ggplot(data=temp_plot,aes(y=Power,x=Group))+geom_col(aes(fill=Method),position="dodge")+
  labs(title=temp)+ylim(0,1)

```






