---
title: "7-20"
output: html_document
---

#Load data and package
```{r}
SEED <- 2019
library(scCB2)
library(DropletUtils)

load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/MALT.RData")
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/PBMC8K.RData")
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/mbrain1K.RData")
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/placenta.RData")
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/Alzheimer.RData")
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/T293.RData")
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/jurkat.RData")
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/PanT4K.RData")
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/PBMC4K.RData")
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/mbrain.RData")
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/PBMC33K.RData")

source("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/functions_forSim.R")

sessionInfo()
```


#Run simulation under easy setting

Under easy setting, part of genes in real cells are shuffled so that they are more different from background, making them easier to be tested out. Set `new_sim=T`.


#Run simulation under hard setting (no shuffling genes)

Under hard setting, genes in simulated real cells are not shuffled. This is closer to real world. Set `new_sim=F`.


```{r}

######################
set.seed(SEED)
mbrain_SIM <- SIM2(dat = mbrain_r, ED_knee = T,new_sim = T,Ncores=6)

set.seed(SEED)
MALT_SIM <- SIM2(dat = MALT_r, ED_knee = T,new_sim = T,Ncores=6)

set.seed(SEED)
PBMC8K_SIM <- SIM2(dat = PBMC8K_r,ED_knee = T,new_sim = T,Ncores=6)

set.seed(SEED)
mbrain1K_SIM <- SIM2(dat = mbrain1K_r,ED_knee = T,new_sim = T,Ncores=6)

set.seed(SEED)
Alz_SIM <- SIM2(dat = Alz_r,ED_knee = T,new_sim = T,Ncores=6)

set.seed(SEED)
T293_SIM <- SIM2(dat = T293_r,ED_knee = T,new_sim = T,Ncores=6)

set.seed(SEED)
PBMC4K_SIM <- SIM2(dat = PBMC4K_r,ED_knee = T,new_sim = T,Ncores=6)

set.seed(SEED)
jurkat_SIM <- SIM2(dat = jurkat_r,ED_knee = T,new_sim = T,Ncores=6)

set.seed(SEED)
PanT4K_SIM <- SIM2(dat = PanT4K_r,ED_knee = T,new_sim = T,Ncores=6)

set.seed(SEED)
PBMC33K_SIM <- SIM2(dat = PBMC33K_r,ED_knee = T,new_sim = T,Ncores=6)

save(MALT_SIM,mbrain_SIM,mbrain1K_SIM,PBMC33K_SIM, PBMC4K_SIM,PBMC8K_SIM,Alz_SIM,
     T293_SIM,jurkat_SIM,PanT4K_SIM,
     file = "~/Google Drive/Hallu/codes/ckgroup/DropletUtils/sim/sim_10_3_new.RData")



```



##plot
```{r}
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/sim/sim_10_3_new.RData")
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/sim/sim_10_3_old.RData")


library(ggplot2)
RED <- "#FF9999"
BLUE <- "#56B4E9"
GREEN <- "#009E73"
YELLOW <- "#F0E442"

Res_list <- list()
Res_list[[1]] <- Alz_SIM
Res_list[[2]] <- jurkat_SIM
Res_list[[3]] <- MALT_SIM
Res_list[[4]] <- mbrain_SIM
Res_list[[5]] <- mbrain1K_SIM
Res_list[[6]] <- PanT4K_SIM
Res_list[[7]] <- PBMC33K_SIM
Res_list[[8]] <- PBMC4K_SIM
Res_list[[9]] <- PBMC8K_SIM
Res_list[[10]] <- T293_SIM



P_diff <- lapply(Res_list,function(x) x$TP_CB2[c(2,4,6),6]-x$TP_ED[c(2,4,6),6])

Size <- lapply(Res_list,function(x) x$Size[,6])
KL_D <- lapply(Res_list,function(x) x$KL_Diver[,6])

Size_knee <- unlist(lapply(Res_list,function(x) x$Size_knee))
KL_knee <- unlist(lapply(Res_list,function(x) x$KL_knee))

ENT <- lapply(Res_list,function(x) x$Ent[,6])
Meta <- data.frame(P_diff=unlist(P_diff),Size=unlist(Size),KL_D=unlist(KL_D),ENT=unlist(ENT))

# plot(Meta)
# summary(lm1 <- lm(P_diff~Size:KL_D,data=Meta))


Meta1 <- Meta[1:10,]
for(i in 1:10){
    Meta1[i,] <- colMeans(Meta[i*3-2:0,])
}

NM <- c("Alzheimer","jurkat","MALT","mbrain9K","mbrain1K","PanT4K","PBMC33K","PBMC4K","PBMC8K","T293")
Meta$Data <- rep(NM,each=3)
Meta$Group <- rep(c("G1","G1.5","G2"),10)


plot(Size~KL_D,data=Meta1)
#points(Meta1$Size[c(4,6,8)]~Meta1$KL_D[c(4,6,8)],col="red")
text(Size ~KL_D, labels=NM,data=Meta1, cex=0.9, font=2)

####knee point large cells
plot(Size_knee~KL_knee)
#points(Meta1$Size[c(4,6,8)]~Meta1$KL_D[c(4,6,8)],col="red")
text(Size_knee~KL_knee, labels=NM, cex=0.9, font=2)

####G1
plot(Meta[1:9*3-2,]$Size~Meta[1:9*3-2,]$KL_D)
#points(Meta1$Size[c(4,6,8)]~Meta1$KL_D[c(4,6,8)],col="red")
text(Meta[1:9*3-2,]$Size~Meta[1:9*3-2,]$KL_D, labels=NM, cex=0.9, font=2)

G1E <- unlist(lapply(Res_list,function(x) x$TP_CB2[2,ncol(x$TP_CB2)]))
G1ED <- unlist(lapply(Res_list,function(x) x$TP_ED[2,ncol(x$TP_ED)]))
G2E <- unlist(lapply(Res_list,function(x) x$TP_CB2[4,ncol(x$TP_CB2)]))
G2ED <- unlist(lapply(Res_list,function(x) x$TP_ED[4,ncol(x$TP_ED)]))
G3E <- unlist(lapply(Res_list,function(x) x$TP_CB2[6,ncol(x$TP_CB2)]))
G3ED <- unlist(lapply(Res_list,function(x) x$TP_ED[6,ncol(x$TP_ED)]))
FDR_E <- unlist(lapply(Res_list,function(x) x$Stat[2,1]))
FDR_ED <- unlist(lapply(Res_list,function(x) x$Stat[2,2]))
Power_Inc <- unlist(lapply(Res_list,function(x) x$Power_diff))

# G1E <- unlist(lapply(Res_list,function(x) x$TP_CB2_adj[2,ncol(x$TP_CB2_adj)]))
# G1ED <- unlist(lapply(Res_list,function(x) x$TP_ED_adj[2,ncol(x$TP_ED_adj)]))
# G2E <- unlist(lapply(Res_list,function(x) x$TP_CB2_adj[4,ncol(x$TP_CB2_adj)]))
# G2ED <- unlist(lapply(Res_list,function(x) x$TP_ED_adj[4,ncol(x$TP_ED_adj)]))
# G3E <- unlist(lapply(Res_list,function(x) x$TP_CB2_adj[6,ncol(x$TP_CB2_adj)]))
# G3ED <- unlist(lapply(Res_list,function(x) x$TP_ED_adj[6,ncol(x$TP_ED_adj)]))
# FDR_E <- unlist(lapply(Res_list,function(x) x$Stat_adj[2,1]))
# FDR_ED <- unlist(lapply(Res_list,function(x) x$Stat_adj[2,2]))
# Power_Inc <- unlist(lapply(Res_list,function(x) x$Power_diff_adj))


plot(rep(2,length(NM))~factor(NM),ylim=c(0,1),ylab="power",xlab=NULL)
lines(G1E~factor(NM),col=RED)
lines(G1ED~factor(NM),col=GREEN)
lines(G2E~factor(NM),col=RED,lty=2)
lines(G2ED~factor(NM),col=GREEN,lty=2)
lines(G3E~factor(NM),col=RED,lty=3)
lines(G3ED~factor(NM),col=GREEN,lty=3)
legend("bottomleft",lty=c(1,1,1,2,3),col=c(RED,GREEN,"black","black","black"),legend=c("CB2","EmptyDrops","G1 (large)","G1.5 (medium)","G2 (small)"),cex = 0.7)

plot(rep(200,length(NM))~factor(NM),ylim=range(Power_Inc)*100,ylab="power diff (%) (CB2 - ED)",xlab=NULL)
lines(Power_Inc*100~factor(NM),col=RED)
abline(h=0,lty=2)
 
plot(rep(100,length(NM))~factor(NM),type="l",ylim=c(0,5),ylab="FDR (%)")
lines(FDR_E*100~factor(NM),col=RED)
lines(FDR_ED*100~factor(NM),col=GREEN)
abline(h=1,lty=2)
legend("topright",lty=1,col=c(RED,GREEN),legend=c("CB2","EmptyDrops"))



```

#Extra functions for drawing plots in CB2 paper
```{r}
#str(G1E)
NM_order <- c("Alzheimer","PBMC8K","PBMC33K", "mbrain1K","mbrain9K","PanT4K","MALT", "PBMC4K","jurkat","T293")


FDR_plot <- data.frame(FDR=c(FDR_E,FDR_ED),Dataset=NM,Method=rep(c("CB2","ED"),each=10))


 tiff(filename ="~/Google Drive/Hallu/codes/ckgroup/DropletUtils/manuscript/Revised/FDR_50.tif",width=30,height=6,units="cm",res=300, compression = "lzw")
ggplot(data=FDR_plot,aes(y=FDR*100,x=Dataset))+geom_col(aes(fill=Method),position="dodge")+geom_hline(yintercept = 1,linetype="dashed")+ylab("FDR (%)")+ylim(c(0,2))+
  scale_x_discrete(limits=(NM_order))+ theme_bw()+theme(axis.text=element_text(size=12),legend.position="none", panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
dev.off()


sim_plot <- data.frame(Power=c(G1E,G1ED,G2E,G2ED,G3E,G3ED),Group=rep(c("G1","G1.5","G2"),each=20), Method=rep(rep(c("CB2","ED"),each=10),3),Dataset=rep(NM,6))

for(temp in NM){
    temp_plot <- sim_plot[sim_plot$Dataset==temp,]
    fname <- paste0("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/manuscript/Revised/Power_150_adj_",temp,".tif")
    tiff(filename =fname,width=3.5,height=8,units="cm",res=300, compression = "lzw")
    gp <- ggplot(data=temp_plot,aes(y=Power,x=Group))+geom_col(aes(fill=Method),position="dodge")+labs(title=temp)+ylim(0,1)+ theme_bw()+ theme(plot.title = element_text(size=12), legend.position = "none", panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+xlab(NULL)
    print(gp)
    dev.off()
}


```



Final KL v.s. Size plot
```{r}
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/sim/sim_10_3_new.RData")

NM <- c("Alzheimer","jurkat","MALT","mbrain9K","mbrain1K","PanT4K","PBMC33K","PBMC4K","PBMC8K","T293")

Res_list <- list()
Res_list[[1]] <- Alz_SIM
Res_list[[2]] <- jurkat_SIM
Res_list[[3]] <- MALT_SIM
Res_list[[4]] <- mbrain_SIM
Res_list[[5]] <- mbrain1K_SIM
Res_list[[6]] <- PanT4K_SIM
Res_list[[7]] <- PBMC33K_SIM
Res_list[[8]] <- PBMC4K_SIM
Res_list[[9]] <- PBMC8K_SIM
Res_list[[10]] <- T293_SIM

Size_new <- unlist(lapply(Res_list,function(x) mean(x$Size[,6])))
KL_new <- unlist(lapply(Res_list,function(x) mean(x$KL_Diver[,6])))

Size_knee <- unlist(lapply(Res_list,function(x) x$Size_knee))
KL_real <- unlist(lapply(Res_list,function(x) x$KL_knee))

load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/sim/sim_10_3_old.RData")


Res_list <- list()
Res_list[[1]] <- Alz_SIM
Res_list[[2]] <- jurkat_SIM
Res_list[[3]] <- MALT_SIM
Res_list[[4]] <- mbrain_SIM
Res_list[[5]] <- mbrain1K_SIM
Res_list[[6]] <- PanT4K_SIM
Res_list[[7]] <- PBMC33K_SIM
Res_list[[8]] <- PBMC4K_SIM
Res_list[[9]] <- PBMC8K_SIM
Res_list[[10]] <- T293_SIM

Size_old <- unlist(lapply(Res_list,function(x) mean(x$Size[,6])))
KL_old <- unlist(lapply(Res_list,function(x) mean(x$KL_Diver[,6])))

KLS <- data.frame(name=NM,KL_new=KL_new,KL_old=KL_old,KL_real=KL_real,
                  Size_new=Size_new,Size_old=Size_old,Size_knee=Size_knee)

gp <- ggplot(data=KLS, aes(x=KL_real))+geom_point(aes(y=KL_old),col=RED)+geom_point(aes(y=KL_new),col=BLUE)+geom_abline(slope = 1,linetype="dashed")+xlim(0,max(KLS$KL_real)*1.2)+ylim(0,max(KLS[,2:3])*1.2)+ theme_bw() + theme(legend.position="none", panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

 tiff(filename ="~/Google Drive/Hallu/codes/ckgroup/DropletUtils/manuscript/Rplots/KL2.tif",width= 10,height=10,units="cm",res=300, compression = "lzw")
 
print(gp)
dev.off()

 tiff(filename ="~/Google Drive/Hallu/codes/ckgroup/DropletUtils/manuscript/Rplots/KL1.tif",width=50,height=10,units="cm",res=300, compression = "lzw")

gp <- ggplot(data=KLS) + xlim(c(0,0.35))+ geom_text(aes(x=KL_new,y=Size_new,label=paste0(name,".IB"),color=name),hjust=0.5, vjust=0.5,size=3) + geom_text(aes(x=KL_old,y=Size_old,label=paste0(name,".IA"),color=name),hjust=0.5, vjust=0.5,size=3)  + xlab("KL divergence") + ylab("Size") + geom_vline(aes(xintercept=KL_real,color=name),linetype="dashed")+ theme_bw() + theme(legend.position="none", panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

print(gp)
dev.off()

```

# Revision: Check the performance of simple hard threshold

```{r}

######################
Prop <- c(0.9,0.5)

set.seed(SEED)
mbrain_HARD <- list()
for(i in seq_along(Prop)){
    mbrain_HARD[[i]] <- SIM_HARD(dat = mbrain_r, ED_knee = T,inflection_prop = Prop[i])
}

set.seed(SEED)
MALT_HARD <- list()
for(i in seq_along(Prop)){
   MALT_HARD[[i]] <- SIM_HARD(dat = MALT_r, ED_knee = T,inflection_prop = Prop[i])
}

set.seed(SEED)
PBMC8K_HARD <- list()
for(i in seq_along(Prop)){
   PBMC8K_HARD[[i]] <- SIM_HARD(dat = PBMC8K_r, ED_knee = T,inflection_prop = Prop[i])
}

set.seed(SEED)
mbrain1K_HARD <- list()
for(i in seq_along(Prop)){
   mbrain1K_HARD[[i]] <- SIM_HARD(dat = mbrain1K_r, ED_knee = T,inflection_prop = Prop[i])
}

set.seed(SEED)
Alz_HARD <- list()
for(i in seq_along(Prop)){
   Alz_HARD[[i]] <- SIM_HARD(dat = Alz_r, ED_knee = T,inflection_prop = Prop[i])
}


set.seed(SEED)
T293_HARD <- list()
for(i in seq_along(Prop)){
   T293_HARD[[i]] <- SIM_HARD(dat = T293_r, ED_knee = T,inflection_prop = Prop[i])
}

set.seed(SEED)
PBMC4K_HARD <- list()
for(i in seq_along(Prop)){
   PBMC4K_HARD[[i]] <- SIM_HARD(dat = PBMC4K_r, ED_knee = T,inflection_prop = Prop[i])
}


set.seed(SEED)
jurkat_HARD <- list()
for(i in seq_along(Prop)){
   jurkat_HARD[[i]] <- SIM_HARD(dat = jurkat_r, ED_knee = T,inflection_prop = Prop[i])
}


set.seed(SEED)
PanT4K_HARD <- list()
for(i in seq_along(Prop)){
   PanT4K_HARD[[i]] <- SIM_HARD(dat = PanT4K_r, ED_knee = T,inflection_prop = Prop[i])
}


set.seed(SEED)
PBMC33K_HARD <- list()
for(i in seq_along(Prop)){
   PBMC33K_HARD[[i]] <- SIM_HARD(dat = PBMC33K_r, ED_knee = T,inflection_prop = Prop[i])
}


save(MALT_HARD,mbrain_HARD,mbrain1K_HARD,PBMC33K_HARD, PBMC4K_HARD,PBMC8K_HARD,Alz_HARD,
     T293_HARD,jurkat_HARD,PanT4K_HARD,
     file = "~/Google Drive/Hallu/codes/ckgroup/DropletUtils/sim/sim_2_8_HARD_Threshold.RData")



```

```{r}
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/sim/sim_2_8_HARD_Threshold.RData")
NM <- c("Alzheimer","jurkat","MALT","mbrain9K","mbrain1K","PanT4K","PBMC33K","PBMC4K","PBMC8K","T293")

HARD_list <- list()
HARD_list[[1]] <- Alz_HARD
HARD_list[[2]] <- jurkat_HARD
HARD_list[[3]] <- MALT_HARD
HARD_list[[4]] <- mbrain_HARD
HARD_list[[5]] <- mbrain1K_HARD
HARD_list[[6]] <- PanT4K_HARD
HARD_list[[7]] <- PBMC33K_HARD
HARD_list[[8]] <- PBMC4K_HARD
HARD_list[[9]] <- PBMC8K_HARD
HARD_list[[10]] <- T293_HARD

Prop <- c(0.9,0.5)
HARD_power <- matrix(0,length(Prop),length(NM))
colnames(HARD_power) <- c(NM)
rownames(HARD_power) <- Prop

HARD_FDR <- HARD_power

for(i in seq_along(HARD_list)){
    HARD_power[,i] <- unlist(lapply(HARD_list[[i]],function(x) x$Stat[1,1]))
    HARD_FDR[,i] <- unlist(lapply(HARD_list[[i]],function(x) x$Stat[2,1]))
}

HARD_melt <- cbind(melt(HARD_FDR,measure.vars=1:10,
                  value.name = "FDR",factorsAsStrings=F),
                  melt(HARD_power,measure.vars=1:10,
                  value.name = "power")[,3])
colnames(HARD_melt) <- c("Prop","dataset","FDR","power")


load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/sim/sim_10_3_old.RData")


Res_list <- list()
Res_list[[1]] <- Alz_SIM
Res_list[[2]] <- jurkat_SIM
Res_list[[3]] <- MALT_SIM
Res_list[[4]] <- mbrain_SIM
Res_list[[5]] <- mbrain1K_SIM
Res_list[[6]] <- PanT4K_SIM
Res_list[[7]] <- PBMC33K_SIM
Res_list[[8]] <- PBMC4K_SIM
Res_list[[9]] <- PBMC8K_SIM
Res_list[[10]] <- T293_SIM
names(Res_list) <- NM

CB2_power <- unlist(lapply(Res_list,function(x) x$Stat[1,1]))
CB2_FDR <- unlist(lapply(Res_list,function(x) x$Stat[2,1]))

CB2_melt <- data.frame(dataset=NM,FDR=CB2_FDR,power=CB2_power)

HARD_melt$PROP <- paste0("10^",seq(0,-2,-0.25))
gp <- ggplot()+geom_line(data=HARD_melt,aes(x=FDR,y=power,col=dataset))+
    geom_vline(xintercept = 0.01)+scale_x_log10()+
    geom_point(data=HARD_melt,aes(x=FDR,y=power,col=dataset))
gp + geom_point(data=CB2_melt,aes(x=FDR,y=power,col=dataset),shape=8)

```

For datasets with very large knee point, most downsampled real cells are still larger than 
inflection point, thus real cells and background barcodes are clearly separated by the 
inflection point. In this case there will be a hard threshold 
performing better than CB2 and ED. E.g. For Alzheimer data, 
knee point = ~9000, inflection point = ~400. Even we downsampled by 10%, G2 cells are still
larger than background barcodes.
In reality if library size is very large, there will accordingly be more ambient 
RNAs inducing large background barcodes. Thus lower the threshold still 
has the risk of including too many background barcodes.


# Revision: Plotting
```{r}
FDR_plot <- data.frame(FDR=c(CB2_FDR,HARD_FDR[1,],HARD_FDR[2,]),
                       Dataset=NM,Method=rep(c("CB2","0.9","0.5"),each=10))

NM_order <- c("Alzheimer","PBMC8K","PBMC33K", "mbrain1K","mbrain9K","PanT4K","MALT", "PBMC4K","jurkat","T293")
ggplot(data=FDR_plot,aes(y=FDR*100,x=Dataset))+geom_col(aes(fill=Method),position="dodge")+geom_hline(yintercept = 1,linetype="dashed")+ylab("FDR (%)")+ylim(c(0,70))+
  scale_x_discrete(limits=(NM_order))+ theme_bw()+theme(axis.text=element_text(size=12), panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

Power_plot <- data.frame(Power=c(CB2_power,HARD_power[1,],HARD_power[2,]),
                       Dataset=NM,Method=rep(c("CB2","0.9","0.5"),each=10))
ggplot(data=Power_plot,aes(y=Power,x=Dataset))+geom_col(aes(fill=Method),position="dodge")+
    ylab("Power")+ylim(c(0,1))+scale_x_discrete(limits=(NM_order))+ theme_bw()+theme(axis.text=element_text(size=12), panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

```

# Revision: Try different lower threshold (50, 150)

Under hard setting, genes in simulated real cells are not shuffled. This is closer to real world. Set `new_sim=F`.


```{r}

######################
set.seed(SEED)
mbrain_SIM <- SIM2(dat = mbrain_r, ED_knee = T,new_sim = F,Ncores=6, threshold = 50)

set.seed(SEED)
MALT_SIM <- SIM2(dat = MALT_r, ED_knee = T,new_sim = F,Ncores=6, threshold = 50)

set.seed(SEED)
PBMC8K_SIM <- SIM2(dat = PBMC8K_r,ED_knee = T,new_sim = F,Ncores=6, threshold = 50)

set.seed(SEED)
mbrain1K_SIM <- SIM2(dat = mbrain1K_r,ED_knee = T,new_sim = F,Ncores=6, threshold = 50)

set.seed(SEED)
Alz_SIM <- SIM2(dat = Alz_r,ED_knee = T,new_sim = F,Ncores=6, threshold = 50)

set.seed(SEED)
T293_SIM <- SIM2(dat = T293_r,ED_knee = T,new_sim = F,Ncores=6, threshold = 50)

set.seed(SEED)
PBMC4K_SIM <- SIM2(dat = PBMC4K_r,ED_knee = T,new_sim = F,Ncores=6, threshold = 50)

set.seed(SEED)
jurkat_SIM <- SIM2(dat = jurkat_r,ED_knee = T,new_sim = F,Ncores=6, threshold = 50)

set.seed(SEED)
PanT4K_SIM <- SIM2(dat = PanT4K_r,ED_knee = T,new_sim = F,Ncores=6, threshold = 50)

set.seed(SEED)
PBMC33K_SIM <- SIM2(dat = PBMC33K_r,ED_knee = T,new_sim = F,Ncores=6, threshold = 50)

save(MALT_SIM,mbrain_SIM,mbrain1K_SIM,PBMC33K_SIM, PBMC4K_SIM,PBMC8K_SIM,Alz_SIM,
     T293_SIM,jurkat_SIM,PanT4K_SIM,
     file = "~/Google Drive/Hallu/codes/ckgroup/DropletUtils/sim/sim_2_24_50.RData")

######################
set.seed(SEED)
mbrain_SIM <- SIM2(dat = mbrain_r, ED_knee = T,new_sim = F,Ncores=6, threshold = 150)

set.seed(SEED)
MALT_SIM <- SIM2(dat = MALT_r, ED_knee = T,new_sim = F,Ncores=6, threshold = 150)

set.seed(SEED)
PBMC8K_SIM <- SIM2(dat = PBMC8K_r,ED_knee = T,new_sim = F,Ncores=6, threshold = 150)

set.seed(SEED)
mbrain1K_SIM <- SIM2(dat = mbrain1K_r,ED_knee = T,new_sim = F,Ncores=6, threshold = 150)

set.seed(SEED)
Alz_SIM <- SIM2(dat = Alz_r,ED_knee = T,new_sim = F,Ncores=6, threshold = 150)

set.seed(SEED)
T293_SIM <- SIM2(dat = T293_r,ED_knee = T,new_sim = F,Ncores=6, threshold = 150)

set.seed(SEED)
PBMC4K_SIM <- SIM2(dat = PBMC4K_r,ED_knee = T,new_sim = F,Ncores=6, threshold = 150)

set.seed(SEED)
jurkat_SIM <- SIM2(dat = jurkat_r,ED_knee = T,new_sim = F,Ncores=6, threshold = 150)

set.seed(SEED)
PanT4K_SIM <- SIM2(dat = PanT4K_r,ED_knee = T,new_sim = F,Ncores=6, threshold = 150)

set.seed(SEED)
PBMC33K_SIM <- SIM2(dat = PBMC33K_r,ED_knee = T,new_sim = F,Ncores=6, threshold = 150)

save(MALT_SIM,mbrain_SIM,mbrain1K_SIM,PBMC33K_SIM, PBMC4K_SIM,PBMC8K_SIM,Alz_SIM,
     T293_SIM,jurkat_SIM,PanT4K_SIM,
     file = "~/Google Drive/Hallu/codes/ckgroup/DropletUtils/sim/sim_2_24_150.RData")


```

