---
title: "9-18"
author: "Zijian Ni"
output: html_document
---

Alzheimer study:

Human brain cells from Prefrontal Cortex zone. 48 samples. Two conditions: AD-pathology v.s. control.


```{r,warning=F,message=F,echo=F}
SEED=2019
RED="#FF9999"
BLUE="#56B4E9"
GREEN="#009E73"
YELLOW="#F0E442"
library(scCB2)
suppressMessages(library(DropletUtils))
library(ggplot2)
library(Rtsne)
suppressMessages(library(dendextend))
suppressMessages(library(Matrix))
library(grid)
suppressMessages(library(edgeR))
library(reshape2)
suppressMessages(library(gplots))
library(scran)
library(irlba)
library(scater)
library(Seurat)

source("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/functions_forReal.R")

load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/Alzheimer.RData")

Groups <- as.integer(gsub(".*-([d]*)","\\1",colnames(Alz_r)))

Alz_knee <- Calc_retain(Alz_r,lower=100)$knee #8136

# set.seed(SEED)
# AlzAll_CB2Out <- CB2FindCell(Alz_r,Ncores = 6,retain = Alz_knee)
# AlzAll_CB2 <- GetCellMat(AlzAll_CB2Out)
# 
# 
# set.seed(SEED)
# eOut <- emptyDrops(Alz_r,lower=100, retain = Alz_knee)
# AlzAll_ED <- Alz_r[,ifelse(is.na(eOut$FDR),FALSE,eOut$FDR<=0.01)]
# save(AlzAll_CB2,AlzAll_ED,file = "~/Google Drive/Hallu/codes/ckgroup/DropletUtils/threshold_100/package/AlzAll_CB2_ED.RData")


load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/threshold_100/package/AlzAll_CB2_ED.RData")
```

##Unique Cells in Alz

```{r,echo=F}
cat("Compare between CB2 and ED\n")
diff_Alz <- barcode_diff(AlzAll_CB2,AlzAll_ED)
cat("below knee point comparison: \n")
diff_Alz_knee <- barcode_diff(AlzAll_CB2[,Matrix::colSums(AlzAll_CB2)<Alz_knee],AlzAll_ED[,Matrix::colSums(AlzAll_ED)<Alz_knee])
```


##normalization
```{r,echo=F}
# Ent_mat1 <- Alz_r[,diff_Alz$CB2_only]
# 
# com_mat1 <- Alz_r[,diff_Alz$Common_b]
# 
# ED_mat1 <- Alz_r[,diff_Alz$ED_only]
# 
# 
# set.seed(SEED)
# sce <- SingleCellExperiment(list(counts=cbind(Ent_mat1,com_mat1,ED_mat1)))
# clusters <- quickCluster(sce, min.size=100)
# sce <- computeSumFactors(sce, cluster=clusters)
# sce <- normalize(sce)
# 
# Alz_f <- sce@assays$data$logcounts
# str(Alz_f)
# colnames(Alz_f) <- colnames(sce@assays$data$counts)
# rownames(Alz_f) <- rownames(sce@assays$data$counts)
# 
# save(Alz_f,file="~/Google Drive/Hallu/codes/ckgroup/DropletUtils/threshold_100/package/Alz_f.RData")

load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/threshold_100/package/Alz_f.RData")
```


##Alz

```{r,warning=F,message=F,echo=F}
# Ent_mat1 <- Alz_f[,diff_Alz$CB2_only[diff_Alz$CB2_only%in%colnames(Alz_f)]]
# 
# com_mat1 <- Alz_f[,diff_Alz$Common_b[diff_Alz$Common_b%in%colnames(Alz_f)]]
# 
# ED_mat1 <- Alz_f[,diff_Alz$ED_only[diff_Alz$ED_only%in%colnames(Alz_f)]]
# 
# Alz_S <- CreateSeuratObject(counts = cbind(com_mat1,ED_mat1, Ent_mat1), project = "Alz")
# set.seed(SEED)
# Alz_S <- FindVariableFeatures(Alz_S, selection.method = "vst", nfeatures = 4000)
# 
# Alz_S <- ScaleData(Alz_S)
# Alz_S <- RunPCA(Alz_S, features = VariableFeatures(object = Alz_S))
# 
# #Alz_S <- FindClusters(Alz_S, algorithm = 3, n.start = 50, n.iter = 50)
# Alz_S <- FindNeighbors(Alz_S, dims = 1:50)
# Alz_S <- FindClusters(Alz_S,n.start = 50, n.iter = 50)
# 
# set.seed(SEED)
# Alz_S <- RunTSNE(Alz_S, dims = 1:50)
# DimPlot(Alz_S, reduction = "tsne")
# 

# Unique_percent <- c()
# for(cc in unique(Alz_S$seurat_clusters)){
#     Sub <- names(Alz_S$seurat_clusters)[Alz_S$seurat_clusters==cc]
#     Unique_percent <- c(Unique_percent, sum(Sub%in%diff_Alz$CB2_only)/length(Sub))
# }
# names(Unique_percent) <- unique(Alz_S$seurat_clusters)
# round(Unique_percent[order(as.integer(names(Unique_percent)))],3)
# sum(Unique_percent>=0.9)

#table(Alz_S$seurat_clusters)



# head(Alz_tsne_n)
# Alz_tsne_n1 <- as.data.frame(Alz_S@reductions$tsne@cell.embeddings)
# Alz_tsne_n1 <- cbind(Alz_tsne_n1,c(rep("Common",ncol(com_mat1)),
#                                        rep("ED_only",ncol(ED_mat1)),
#                                    rep("CB2_only",ncol(Ent_mat1))))
# 
# 
# colnames(Alz_tsne_n1) <- c("tSNE1","tSNE2","Group")
# Alz_tsne_n1$Group <- as.character(Alz_tsne_n1$Group)
# Alz_tsne_n1$Cluster[names(Alz_S$seurat_clusters)] <- as.character(Alz_S$seurat_clusters)
# Condition <- as.integer(unlist(lapply(strsplit(rownames(Alz_tsne_n1),split = "-"),function(x) x[2])))%%2
# 
# Alz_tsne_n1$Condition <- ifelse(Condition == 1, "Control", "AD-pathology")

#
#save(Alz_tsne_n1,file="~/Google Drive/Hallu/codes/ckgroup/DropletUtils/threshold_100/package/Alz_tsne1.RData")
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/threshold_100/package/Alz_tsne1.RData")


tiff(filename ="~/Google Drive/Hallu/codes/ckgroup/DropletUtils/manuscript/Rplots/Alz_tSNE.tif",width=22,height=20,units="cm",res=300,pointsize=10, compression = "lzw")
ggplot(Alz_tsne_n1)+geom_point(aes(x=tSNE1,y=tSNE2,color=Group),size=0.05)+
  scale_color_manual(values=c("deeppink3","yellow","deeppink1","black"))+ theme_bw() +
    guides(colour = guide_legend(override.aes = list(size=2)))+ 
    theme(axis.text = element_blank(),axis.title = element_blank(),legend.position = "none",panel.border = element_rect(colour = "black", fill=NA, size=1.5), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
dev.off()

ggplot(Alz_tsne_n1)+geom_point(aes(x=tSNE1,y=tSNE2,color=Condition),size=0.05)


tiff(filename ="~/Google Drive/Hallu/codes/ckgroup/DropletUtils/manuscript/Rplots/Alz_Cluster.tif",width=25,height=20,units="cm",res=300,pointsize=10, compression = "lzw")

ggplot(Alz_tsne_n1)+geom_point(aes(x=tSNE1,y=tSNE2,color=Cluster),size=0.05)+
  scale_color_discrete(breaks=unique(Alz_tsne_n1$Cluster))+ guides(colour = guide_legend(override.aes = list(size=2)))+ theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

dev.off()

#names(which(colSums(Alz_r[,colnames(Alz_f)])<200))
ggplot(Alz_tsne_n1[names(which(colSums(Alz_r[,colnames(Alz_f)])<200)),])+geom_point(aes(x=tSNE1,y=tSNE2,color=Group),size=0.05)+
  scale_color_manual(values=c("yellow","deeppink1","black"))+ theme_bw() +
    guides(colour = guide_legend(override.aes = list(size=2)))+ 
    theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
    xlim(min(Alz_tsne_n1$tSNE1),max(Alz_tsne_n1$tSNE1))+ylim(min(Alz_tsne_n1$tSNE2),max(Alz_tsne_n1$tSNE2))


mk_plot("count", dat_tsne_n1 = Alz_tsne_n1, dat_f=cbind(com_mat1,ED_mat1))  

```



distribution plot
```{r}
C2 <- rownames(Alz_tsne_n1)[check_range(Alz_tsne_n1$y,15,31) & check_range(Alz_tsne_n1$x,10,17)]

C3 <- rownames(Alz_tsne_n1)[check_range(Alz_tsne_n1$y,31,41) & check_range(Alz_tsne_n1$x,5,15)]

C4 <- rownames(Alz_tsne_n1)[check_range(Alz_tsne_n1$y,-1,5) & check_range(Alz_tsne_n1$x,23,29)]

MK_gene <- c("SYT1","SNAP25","GRIN1","SLC17A7","CAMK2A","NRGN","GAD1","GAD2","MBP","MOBP","PLP1","CD74","CSF1R","C3","AQP4","GFAP","FAM107A","SOX9","PDGFRA","VCAN","CSPG4","FLT1","CLDN5")
C_cand <- c(2,3,4,6,7,8,9,12,13,14,15,16,17,19,20)
C_cand <- c(20)

for(CC in C_cand){
    fname <- paste0("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/manuscript/Rplots/Alz/Alz_newColor_C",CC)
    
    Alz_sub <- Alz_f[,rownames(Alz_tsne_n1)[Alz_tsne_n1$Cluster==CC]]
    n_temp <- names(sort(Matrix::rowMeans(Alz_sub),decreasing = T)[1:500] )

    tiff(filename =paste0(fname,"_D_%03d.tif"),width=10,height=5,units="cm",res=300,pointsize=10, compression = "lzw")
    Htmap(Alz_r[sort(filter_mr(setdiff(n_temp,"MALAT1"))[1:100]),colnames(Alz_sub)],"Alz", Plot = "D", AddBackground = F)
    dev.off()

    # tiff(filename =paste0(fname,"_D_marker_%03d.tif"),width=10,height=5,units="cm",res=300,pointsize=10, compression = "lzw")
    # Htmap(Alz_r[MK_gene,rownames(Alz_tsne_n1)[Alz_tsne_n1$Cluster==CC]],"Alz",Plot = "D")
    # dev.off()
    
    # tiff(filename =paste0(fname,"_H.tif"),width=15,height=15,units="cm",res=300,pointsize=10, compression = "lzw")
    # Htmap(Alz_r[sort(filter_mr(setdiff(n_temp,"MALAT1"))[1:100]),colnames(Alz_sub)],"Alz", Plot = "H")
    # dev.off()
    
    # tiff(filename =paste0(fname,"_H_marker.tif"),width=10,height=10,units="cm",res=300,pointsize=10, compression = "lzw")
    # Htmap(Alz_r[MK_gene,rownames(Alz_tsne_n1)[Alz_tsne_n1$Cluster==CC]],"Alz", Plot = "H")
    # dev.off()
}

Htmap(Alz_r[MK_gene,rownames(Alz_tsne_n1)[Alz_tsne_n1$Cluster==19]],"Alz")

Alz_sub <- Alz_f[,rownames(Alz_tsne_n1)[Alz_tsne_n1$Cluster==9]] #303 ,209 CB2 only
n_temp <- names(sort(Matrix::rowMeans(Alz_sub),decreasing = T)[1:500] )
Htmap(Alz_r[sort(filter_mr(setdiff(n_temp,"MALAT1"))[1:100]),colnames(Alz_sub)],"Alz")
```


###marker gene
```{r}
MK_gene2 <- MK_gene
for(GG in MK_gene2){
    print(GG)
    tiff(filename =paste0("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/manuscript/Rplots/Alz/Alz_newColor_",GG,"_CB2.tif"),width=15,height=12,units="cm",res=300,pointsize=10, compression = "lzw")
    mk_plot(GG,diff_dat = diff_Alz, dat_tsne_n1 = Alz_tsne_n1,dat_f = Alz_f, CB2=T)
    dev.off()
}

#FAM107A
#SOX9

mk_plot("DHFR",diff_dat = diff_Alz, dat_tsne_n1 = Alz_tsne_n1,dat_f = Alz_f, CB2=T)
```



###Relook at CB2 + ED. Follow data processing steps in the Alzheimer paper.
```{r}
Alz_CB2 <- c(diff_Alz$Common_b,diff_Alz$CB2_only)
Alz_ED <- c(diff_Alz$Common_b,diff_Alz$ED_only)

Alz_fall <- unique(c(Alz_CB2,Alz_ED))


#Filter out high mitochondrial cells
Alz_MT <- colSums(Alz_r[,Alz_fall][grep("\\<MT-",rownames(Alz_r)),])
Alz_MTprop <- Alz_MT/colSums(Alz_r[,Alz_fall])

Alz_fall3 <- Alz_fall[Alz_MTprop<=0.4]


# # Redo normalization
# set.seed(SEED)
# km <- kmeans(Alz_MTprop,centers = 2)$cluster
# Alz_fall2 <- names(km)[km==1]

# set.seed(SEED)
# sce <- SingleCellExperiment(list(counts=Alz_r[rowSums(Alz_r[,Alz_fall3]>0)>=2,Alz_fall3]))
# clusters <- quickCluster(sce,min.size=100)
# sce <- computeSumFactors(sce, cluster=clusters, positive=FALSE)
# Neg <- which(sce@int_colData$size_factor<=0)
# sce@int_colData$size_factor[Neg] <- sort(sce@int_colData$size_factor[-Neg])[1]/10
# 
# sce <- normalize(sce)
# 
# Alz_fAll3 <- sce@assays$data$logcounts
# 
# colnames(Alz_fAll3) <- colnames(sce@assays$data$counts)
# rownames(Alz_fAll3) <- rownames(sce@assays$data$counts)

#save(Alz_fAll3,file="~/Google Drive/Hallu/codes/ckgroup/DropletUtils/threshold_100/package/Alz_f_All3.RData")
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/threshold_100/package/Alz_f_All3.RData")

# Alz_S <- CreateSeuratObject(counts = Alz_fAll3, project = "Alz")
# set.seed(SEED)
# Alz_S <- FindVariableFeatures(Alz_S, selection.method = "vst", nfeatures = 4000)
# Alz_S <- ScaleData(Alz_S)
# Alz_S <- RunPCA(Alz_S, features = VariableFeatures(object = Alz_S))
# Alz_S <- FindNeighbors(Alz_S, dims = 1:50)
# Alz_S <- FindClusters(Alz_S,n.start = 50, n.iter = 50)

# set.seed(SEED)
# Alz_S <- RunTSNE(Alz_S, dims = 1:50)
# 
# Alz_tsne3_all <- as.data.frame(Alz_S@reductions$tsne@cell.embeddings)
# 
# colnames(Alz_tsne3_all) <- c("tSNE1","tSNE2")
# Alz_tsne3_all$Cluster <- as.character(Alz_S$seurat_clusters)
# 
# Condition <- as.integer(unlist(lapply(strsplit(rownames(Alz_tsne3_all),split = "-"),function(x) x[2])))%%2
# # 
# Alz_tsne3_all$Condition <- ifelse(Condition == 1, "Control", "AD-pathology")
# Alz_tsne3_all[names(Alz_S$seurat_clusters),]$Cluster <- as.character(Alz_S$seurat_clusters)
# Alz_tsne3_all$Group <- "common"
# Alz_tsne3_all$Group[rownames(Alz_tsne3_all)%in%setdiff(Alz_CB2,Alz_ED)] <- "CB2_only"
# Alz_tsne3_all$Group[rownames(Alz_tsne3_all)%in%setdiff(Alz_ED,Alz_CB2)] <- "ED_only"

```


##DE analysis of Excitatory and Inhibitory Neurons.
```{r}
# MK_gene2 <- c("SYT1","SLC17A7", "GAD1","GAD2","GFAP","MBP", "CD74","PDGFRA","FLT1")
# for(GG in MK_gene2){
#     print(GG)
#     tiff(filename =paste0("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/manuscript/Rplots/Alz/NEW_Alz_",GG,".tif"),width=15,height=12,units="cm",res=300,pointsize=10, compression = "lzw")
#     mk_plot(GG,diff_dat = diff_Alz, dat_tsne_n1 = Alz_tsne3_all,dat_f = Alz_fAll3, CB2=F)
#     dev.off()
# }

# Alz_tsne3_all$celltype <- "ExN"
# 
# Alz_tsne3_all$celltype[Alz_tsne3_all$Cluster%in%c(0,2)] <- "Olig"
# Alz_tsne3_all$celltype[Alz_tsne3_all$Cluster%in%c(27) & check_range(Alz_tsne3_all$tSNE1,5,20)] <- "GFAP+Olig"
# Alz_tsne3_all$celltype[Alz_tsne3_all$Cluster%in%c(11) ] <- "OPC"
# Alz_tsne3_all$celltype[Alz_tsne3_all$Cluster%in%c(6) |Alz_tsne3_all$Cluster%in%c(28) & check_range(Alz_tsne3_all$tSNE2,15,30) | Alz_tsne3_all$Cluster%in%c(27) & check_range(Alz_tsne3_all$tSNE1,-20,5)] <- "Ast"
# Alz_tsne3_all$celltype[Alz_tsne3_all$Cluster%in%c(12)] <- "Mic"
# Alz_tsne3_all$celltype[Alz_tsne3_all$Cluster%in%c(22) & check_range(Alz_tsne3_all$tSNE1,0,12)] <- "End"
# Alz_tsne3_all$celltype[Alz_tsne3_all$Cluster%in%c(9,13,15,18,23)] <- "InN"

#save(Alz_tsne3_all,file="~/Google Drive/Hallu/codes/ckgroup/DropletUtils/threshold_100/package/Alz_tsne3_all.RData")
load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/threshold_100/package/Alz_tsne3_all.RData")

ggplot(Alz_tsne3_all)+geom_point(aes(x=tSNE1,y=tSNE2,color=celltype),size=0.05)+ guides(colour = guide_legend(override.aes = list(size=2)))+ theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))




# FC_ExN <- as.data.frame(matrix(0,9,5))
# FC_ExN[,5] <- c("GOLT1B","ATF6B","DDRGK1","TUBB2A","BEX2","ATPIF1","RASGEF1B","NGFRAP1","LINGO1")
# colnames(FC_ExN) <- c("CB2 (logFC)","ED (logFC)", "CB2 (pval)","ED (pval)", "id")
# 
# for(i in seq_len(nrow(FC_ExN))){
#     gene_tmp <- FC_ExN[i,5]
#     t_CB2 <- DE(celltype = "ExN",gene=gene_tmp, tsne=Alz_tsne3_all[rownames(Alz_tsne3_all)%in%Alz_CB2,],  diff= F, prop = F)
#     t_ED <- DE(celltype = "ExN",gene=gene_tmp, tsne=Alz_tsne3_all[rownames(Alz_tsne3_all)%in%Alz_ED,],  diff= F, prop = F)
# 
#     FC_ExN[i,1] <- t_CB2$log2FC
#     FC_ExN[i,2] <- t_ED$log2FC
# 
#     FC_ExN[i,3] <- t_CB2$pval
#     FC_ExN[i,4] <- t_ED$pval
# }
# 
# 
# 
# FC_InN <- as.data.frame(matrix(0,9,5))
# FC_InN[,5] <- c("TCEAL4","SPCS1","FBXO2","COX4I1","ATPIF1","SOD1","NGFRAP1","TMSB4X","NDUFA4")
# colnames(FC_InN) <- c("CB2 (logFC)","ED (logFC)", "CB2 (pval)","ED (pval)", "id")
# 
# 
# for(i in seq_len(nrow(FC_InN))){
#     gene_tmp <- FC_InN[i,5]
#     t_CB2 <- DE(celltype = "InN",gene=gene_tmp, tsne=Alz_tsne3_all[rownames(Alz_tsne3_all)%in%Alz_CB2,],  diff= F, prop = F)
#     t_ED <- DE(celltype = "InN",gene=gene_tmp, tsne=Alz_tsne3_all[rownames(Alz_tsne3_all)%in%Alz_ED,],  diff= F, prop = F)
# 
#     FC_InN[i,1] <- t_CB2$log2FC
#     FC_InN[i,2] <- t_ED$log2FC
# 
#     FC_InN[i,3] <- t_CB2$pval
#     FC_InN[i,4] <- t_ED$pval
# }
# 
# save(FC_ExN,FC_InN, file="~/Google Drive/Hallu/codes/ckgroup/DropletUtils/threshold_100/package/Alz_DE_new.RData")

load("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/threshold_100/package/Alz_DE_new.RData")

ExN_p <- melt(FC_ExN[,3:5],id.vars="id")
 tiff(filename =paste0("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/manuscript/Rplots/Alz/Alz_DE_ExN_pval.tif"),width=18,height=9,units="cm",res=300,pointsize=10, compression = "lzw")
ggplot(ExN_p, aes(x=id, y=value, fill=variable)) +
    geom_bar(stat='identity', position='dodge')+ theme_bw() + theme(axis.text=element_text(size=10),axis.title.y = element_blank(),axis.title.x = element_blank(),legend.position = "none",panel.border = element_rect(colour = "black", fill=NA, size=1.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  scale_x_discrete(limits=FC_ExN$id)
dev.off()


ExN_f <- melt(FC_ExN[,c(1,2,5)],id.vars="id")
 tiff(filename =paste0("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/manuscript/Rplots/Alz/Alz_DE_ExN_logFC.tif"),width=18,height=9,units="cm",res=300,pointsize=10, compression = "lzw")
ggplot(ExN_f, aes(x=id, y=value, fill=variable)) +
    geom_bar(stat='identity', position='dodge') + theme_bw() + theme(axis.text=element_text(size=10),axis.title.y = element_blank(),axis.title.x = element_blank(),legend.position = "none",panel.border = element_rect(colour = "black", fill=NA, size=1.5), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  scale_x_discrete(limits=FC_ExN$id)
dev.off()

InN_p <- melt(FC_InN[,3:5],id.vars="id")
 tiff(filename =paste0("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/manuscript/Rplots/Alz/Alz_DE_InN_pval.tif"),width=18,height=9,units="cm",res=300,pointsize=10, compression = "lzw")

ggplot(InN_p, aes(x=id, y=value, fill=variable)) +
    geom_bar(stat='identity', position='dodge')+ theme_bw() + theme(axis.text=element_text(size=10),axis.title.y = element_blank(),axis.title.x = element_blank(),legend.position = "none",panel.border = element_rect(colour = "black", fill=NA, size=1.5), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  scale_x_discrete(limits=FC_InN$id)
dev.off()

InN_f <- melt(FC_InN[,c(1,2,5)],id.vars="id")
 tiff(filename =paste0("~/Google Drive/Hallu/codes/ckgroup/DropletUtils/manuscript/Rplots/Alz/Alz_DE_InN_logFC.tif"),width=18,height=9,units="cm",res=300,pointsize=10, compression = "lzw")

ggplot(InN_f, aes(x=id, y=value, fill=variable)) +
    geom_bar(stat='identity', position='dodge')+ theme_bw() + theme(axis.text=element_text(size=10), axis.title.y = element_blank(),axis.title.x = element_blank(), legend.position = "none",panel.border = element_rect(colour = "black", fill=NA, size=1.5), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  scale_x_discrete(limits=FC_InN$id)
dev.off()
```


# Revision: Lower the upper threshold to 0.5 * knee_point and see barcodes included

790 more barcodes. 
```{r}
Extra_Alz <- colnames(Alz_r)[colSums(Alz_r)>=0.05*Alz_knee]
Extra_Alz <- setdiff(Extra_Alz,colnames(AlzAll_CB2)) 

Htmap_revision(Extra_Alz,Alz_r, 
            background_threshold=100, AddBackground=F)

```

# Revision: Boxplot of Subpop1~5

```{r}
ggplot(Alz_tsne_n1[Alz_tsne_n1$Cluster%in%c(1:4,6:8,12,14,20),])+geom_point(aes(x=tSNE1,y=tSNE2,color=Cluster),size=0.5)+ guides(colour = guide_legend(override.aes = list(size=5)))

Subpop1 <- c(6)
Subpop2 <- c(1:4)
Subpop3 <- c(7,14)
Subpop4 <- c(8,12)
Subpop5 <- c(20)

Size_list <- list()
Size_list$Subpop1 <- rownames(Alz_tsne_n1)[Alz_tsne_n1$Cluster==6]
Size_list$Subpop2 <- rownames(Alz_tsne_n1)[Alz_tsne_n1$Cluster%in%c(1:4)]
Size_list$Subpop3 <- rownames(Alz_tsne_n1)[Alz_tsne_n1$Cluster%in%c(7,14)]
Size_list$Subpop4 <- rownames(Alz_tsne_n1)[Alz_tsne_n1$Cluster%in%c(8,12)]
Size_list$Subpop5 <- rownames(Alz_tsne_n1)[Alz_tsne_n1$Cluster%in%c(20)]
names(Size_list) <- paste0("Subpop",1:5)

Size_mat <- data.frame(counts=unlist(lapply(Size_list,function(x) colSums(Alz_r[,x]))),
                       Subpopulation=rep(paste0("Subpop",1:5),
                                         unlist(lapply(Size_list,length))),
                       group=ifelse(unlist(Size_list)%in%diff_Alz$CB2_only,"CB2","common"))
Size_mat$subpopulation <- paste0(Size_mat$Subpopulation,"_",Size_mat$group)

ggplot(data=Size_mat)+geom_boxplot(aes(y=counts,x=subpopulation,color=Subpopulation))+scale_y_log10()


```

# Revision: Distribution plot of Subpop5 using 6 marker genes.
```{r}
Htmap(Alz_r[c("GFAP","AQP4","FAM107A","MBP","MOBP","PLP1"),Size_list$Subpop5],"Alz", Plot = "D", AddBackground = F)QP

rowMeans(Alz_r[c("GFAP","AQP4","FAM107A","MBP","MOBP","PLP1"),Size_list$Subpop5])
```